Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-15 talk/pepm2011/paper.tex
Semicolonization.

A further complication is that most interpreters written with PyPy use
heap-allocated frame objects to store local variables. Those severely hinder
the effectiveness of allocation removal, because every time an object is stored
into a local variable, it is stored into the frame-object, which makes it
escape. We implemented a technique to treat such frames objects in a
special way to solve this problem. This is a common approach in VM
implementations \cite{miranda_context_1999,andreas_gal_trace-based_2009}, the
novelty of our approach is that we generalized it enough to be usable for
different interpreter.

>>>>

A further complication is that most interpreters written with PyPy use
heap-allocated frame objects to store local variables. Those severely hinder
the effectiveness of allocation removal, because every time an object is stored
into a local variable, it is stored into the frame-object, which makes it
escape. We implemented a technique to treat such frames objects in a
special way to solve this problem. This is a common approach in VM
implementations \cite{miranda_context_1999,andreas_gal_trace-based_2009}; the
novelty of our approach is that we generalized it enough to be usable for
different interpreter.
